Operational adoption of new probabilistic point rainfall forecasts: the crucial role of a user-centric training

### 2021-01-22 manuscript/main.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%
% Background of ecPoint-Rainfall testers
\section{The background of ecPoint-Rainfall testers}

\subsection{Cost Rica - IMN}

\subsection{Hungary - OMSZ}

@@

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Estimate.png}}
\caption{Relationship between users' understanding (UND) of ensemble-based probabilistic forecasts and their effective (EFF) use in decision-making. Diagram's x-axis represents UND levels: "low", "medium", "high". Over time, training on ensemble-based probabilistic forecasts (green arrow by the x-axis) can push UND from "low" to "medium" or "high" levels. Diagram's y-axis represents EFF levels: "ineffective", "moderately effective", "very effective". Over time, training on how to better communicate ensemble-based probabilistic outputs (green arrow by the y-axis) can push their effectiveness in decision-making from "ineffective" to "moderately effective" or "very effective". The black line represents optimal values for the UND-EFF relationship, and no UND-EFF pairs can exist in the (black dashed) area above the black line. Qualitatively, the blue line represents state-of-the-art UND-EFF relationship for traditional probabilistic ensemble-based forecasts.}
\label{UND_EFF_estimated}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/FlowChart.png}}
\caption{Timeline of the trial phases. The first phase, the "real-time phase", took place between 2018 and 2019 and lasted 12 months. Th second phase, the "offline phase", took place between 2019 and 2021 and lasted 15 months.}
\label{FlowChart}
\end{figure}

\begin{figure*}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/Fig5.png}}
\caption{Materials provided to IMN and OMSZ during the "Real-Time Phase" of the trial. }
\label{Fig5}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%
% Results
\section{Results}

\subsection{Real-time phase}

\subsection{Offline phase}

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Observed.png}}
\caption{Like Fig.\ref{UND_EFF_estimated}, but it includes the results of the experiment with IMN and OMSZ. Such results show that the real gap in the UND-EFF relationship between ecPoint and traditional ensemble-based forecasts (dashed fuchsia area) is greater than it was estimated at the beginning of the experiment as users with different ensemble-based forecasts understanding levels performed similarly in terms of effective use of such forecasts in decision-making processes.}
\label{UND_EFF_observed}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%
% Discussions
\section{Discussions}

@@

%%%%%%%%%%%%%%%%%%%%
% Conclusions
\section{Conclusions}

>>>>

%%%%%%%%%%%%%%%%%%%%
% Background of ecPoint-Rainfall testers

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/GeoLocation_H_CR.png}}
\caption{Panel (a) shows Costa Rica location in Central America and Hungary location in Europe. Panel (b) and (c) show respectively the orography of Costa Rica and Hungary.}
\label{GeoLocation_H_CR}
\end{figure}

\section{Background on Costa Rica}
\subsection{Extreme rainfall climatology in Costa Rica}
\subsection{How does IMN traditionally forecast extreme rainfall events?}

\section{Background on Hungary}
\subsection{Extreme rainfall climatology in Hungary}
\subsection{How does OMSZ traditionally forecast extreme rainfall events?}

@@

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/UND_EFF_TradEPFs.png}}
\caption{Relationship between users' understanding (UND) of ensemble-based probabilistic forecasts and their effective (EFF) use in decision-making. Diagram's x-axis represents UND levels: "low", "medium", "high". Over time, training on ensemble-based probabilistic forecasts (cyan arrow in the x-axis direction) can push UND from "low" to "medium" or "high" levels. Diagram's y-axis represents EFF levels: "ineffective", "moderately effective", "very effective". Over time, training on how to communicate ensemble-based probabilistic outputs (cyan arrow in the y-axis direction) can push their effectiveness in decision-making from "ineffective" to "moderately effective" or "very effective". The green line represents optimal values for the UND-EFF relationship, and no UND-EFF pairs can exist in the green dashed area above the green line. Qualitatively, the blue line represents state-of-the-art UND-EFF relationship for traditional probabilistic ensemble-based forecasts.}
\label{UND_EFF_TradEPFs}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/FlowChart.png}}
\caption{Firstly, the flowchart describes the experiment processes that follow in the two experiment phases (real-time and offline). Secondly, the flowchart describes who, between developers (red squares), testers (blue squares) and developers & testers (cyan squares), conducted the experiment processes. Finally, the flowchart describes the possible experiment outcomes.}
\label{FlowChart}
\end{figure}

\begin{figure*}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/Remote_Training.png}}
\caption{Training material provided to IMN and OMSZ at the beginning of the "Real-Time Phase" of the trial.}
\label{Fig5}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%
% Results
\section{Results: real-time phase}

\subsection{Costa Rica}

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/ProbFC_Knowledge_Effectiveness_Observed.png}}
\caption{Like Fig.\ref{UND_EFF_estimated}, but it includes the results of the experiment with IMN and OMSZ. Such results show that the real gap in the UND-EFF relationship between ecPoint and traditional ensemble-based forecasts (dashed fuchsia area) is greater than it was estimated at the beginning of the experiment as users with different ensemble-based forecasts understanding levels performed similarly in terms of effective use of such forecasts in decision-making processes.}
\label{UND_EFF_observed}
\end{figure}
"

@@

\subsection{Hungary}

\section{Results: offline phase}

@@

%%%%%%%%%%%%%%%%%%%%
% Discussions
\section{Discussion}

%%%%%%%%%%%%%%%%%%%%
% Conclusions
\section{Conclusion}
